\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-11-03 paper/main.tex
tweaks to intro to section 3

Figure~\ref{fig:illustrative-example} illustrates how one might use \texttt{davos} in a real-world setting to facilitate reproducible data analyses. In this scenario, a user has acquired a dataset and pre-trained semantic model (possibly shared by a collaborator, or downloaded from a public repository) with which they want to run a set of analyses in an IPython notebook. The hypothetical dataset (a \texttt{pandas} \cite{McKi10} \texttt{DataFrame}) and model (a \texttt{scikit-learn} \cite{PedrEtal11} \texttt{Pipeline}) were created and saved using the latest versions of each package available in December 2019 and, due to their age and the formats in which they were provided, now pose certain challenges to loading and using them. The code in Figure~\ref{fig:illustrative-example} would be included at the top of the user's analysis notebook, and demonstrates how \texttt{davos} enables them to overcome these issues cleanly and efficiently, while simultaneously constructing a reproducible Python environment that ensures their analyses are always run under the same conditions, both by the user themselves and anyone with whom they share their code.

>>>>

Figure~\ref{fig:illustrative-example} illustrates how one might use \texttt{davos} in a real-world setting to facilitate reproducible data analyses. In this scenario, a user has acquired a dataset and pre-trained semantic model (possibly shared by a collaborator, or downloaded from a public repository) with which they want to run a set of analyses in a Jupyter notebook. The hypothetical dataset (a \texttt{pandas}~\cite{McKi10} \texttt{Panel}) and model (a \texttt{scikit-learn}~\cite{PedrEtal11} \texttt{Pipeline}) were created and saved using the latest versions of each package available in June 2019 and, due to their age and the formats in which they were provided, now pose certain challenges to loading and using them. The code in Figure~\ref{fig:illustrative-example} would be included at the top of the user's analysis notebook, and demonstrates how \texttt{davos} enables them to overcome these issues cleanly and efficiently, while simultaneously constructing a reproducible Python environment that ensures their analyses are always run under the same conditions, both by the user themselves and anyone with whom they share their code.
